04_application

### 2020-01-22 chapters/04_application.Rmd
update script for final fits, some notes thru chapters

@@

>>>>

#### Divergences

After running four chains for 10,000 iterations each, this model does produce some *divergences*. **This means I should explain what a divergence is** To be exact, this model produces 30 divergent transtions out of 20,000 post-warmup transitions, for a divergent rate of 0.15%. Divergencies are a diagnostic particular to the HMC and NUTS samplers used by Stan.

#### Variables Selected

Perhaps surprisingly, the use of  horseshoe priors only suggests the removal of four variables: __, __, __, __. This is likely because the initial set of covariates were selected based on domain knowledge and therefore, it was unlikely for $\beta$ to be exceedingly sparse. The application of the horseshoe prior would be more informative in a data set with more parameters, and with less insight into the selection of the initial covariate vector $x$.

@@

For computational efficiency, we can drop the horseshoe priors for this model. Armed with the information provided by our fist two models, we can simply give $\beta$ tigher normal priors.
